The Bug Catalog of the Maven Ecosystem

### 2014-02-21 docs/msr.tex
changes based on dds' comments

\maketitle
\begin{abstract}
Examining software ecosystems can provide the research community
with useful information. To examine the ecosystem of
the Maven central repository (approximately 265{\sc gb} of data),
we performed an experiment where we statically analyzed the
repository to detect its software bugs. For our analysis we
used FindBugs, a tool that examines Java bytecode to detect
numerous types of bugs. In this paper we present the dataset
that was produced from this experiment.
The dataset contains the metrics results that FindBugs reports for
every project version (a {\sc jar}) included in the ecosystem. For every
version we also stored specific metadata such as the {\sc jar}'s
size, its dependencies and others. Our dataset can be used to produce
interesting research results, as we show in specific examples.
\end{abstract}

@@

A threat to the internal validity of our experiment could be the false
alarms of the FindBugs tool~\cite{AP10}.
Specifically, reported security bugs may not
be applicable to an application's typical use context.
For instance, FindBugs could report an {\sc sql}
injection vulnerability
in an application that receives no external input.
In this particular context, this would be a false
positive alarm.

@@

Note that our experiment can be duplicated
in order to collect metrics results from other tools that
examine Java programs like
{\sc cjkm}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}}
that calculates Chidamber and Kemerer
object-oriented metrics~\cite{CK91},
{\it Java Pathfinder}\footnote{\url{http://babelfish.arc.nasa.gov/trac/jpf/wiki}}
that performs
model checking~\cite{CEES09} on Java bytecode programs,
and others. To achieve this, instead of invoking
FindBugs, our worker can invoke such tools.

>>>>

\maketitle
\begin{abstract}
Examining software ecosystems can provide the research community
with data regarding artifacts, processes, and communities.
We present a dataset obtained from the Maven central repository
ecosystem (approximately 265{\sc gb} of data) by statically analyzing
the repository to detect potential software bugs.
For our analysis we used FindBugs, a tool that examines Java
bytecode to detect numerous types of bugs.
The dataset contains the metrics results that FindBugs reports for
every project version (a {\sc jar}) included in the ecosystem. For every
version we also stored specific metadata such as the {\sc jar}'s
size, its dependencies and others. Our dataset can be used to produce
interesting research results, as we show in specific examples.
\end{abstract}

@@

A threat to the internal validity of our dataset
construction process could be the false
alarms of the FindBugs tool~\cite{AP10}.
Specifically, reported security bugs may not
be applicable to an application's typical use context.
For instance, FindBugs could report an {\sc sql}
injection vulnerability
in an application that receives no external input.
In this particular context, this would be a false
positive alarm.

@@

Note that our data collection process can be duplicated
in order to collect metrics results from other tools that
examine Java programs like
{\sc cjkm}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}}
that calculates Chidamber and Kemerer
object-oriented metrics~\cite{CK91},
{\it Java Pathfinder}\footnote{\url{http://babelfish.arc.nasa.gov/trac/jpf/wiki}}
that performs
model checking~\cite{CEES09} on Java bytecode programs,
and others. To achieve this, instead of invoking
FindBugs, our worker can invoke such tools.
